Measuring starspot properties by forward modeling IGRINS spectra of \name

### 2016-06-28 document/ms.tex
Table of of Stellar properties as a function of order, closes #17

We combined the IGRINS spectrum with the fourth ESPaDoNs spectrum from Table \ref{tbl_estimated_V}.  These spectra have comparable $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.  We chunked the spectra into $N_{ord}=$58 of their cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.  We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:teffOrder}.  The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical.

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/teff_v_wl_example} 
	\caption{Effective temperature as derived by different orders.}
	\label{fig:teffOrder}
\end{figure*}

>>>>

We combined the IGRINS spectrum with the fourth ESPaDoNs spectrum from Table \ref{tbl_estimated_V}.  These spectra have comparable $\hat V$ of 12.90 and 12.83 for the ESPaDoNs and IGRINS spectra respectively.  We chunked the spectra into $N_{ord}=$58 of their cleanest spectral orders and derived the stellar parameters $\vt_{\ast,m}$ independently in each $m^{\mathrm{th}}$ order.  We found 58 unique estimates for $\teff$ as a function of wavelength, which we compile in Figure \ref{fig:SingleTeffvsOrder}.  The derived effective temperature is on-average about 800 K cooler in the $K-$band than in the optical or short-wavelength end of $H-$band.

\begin{figure*}
	\centering
	\includegraphics[width=0.95\textwidth]{figures/single_Teff_v_order}
	\caption{Effective temperature as derived from unique full spectrum fitting to each of 58 spectral orders in the optical through infrared portions of the spectrum assuming a single component photosphere.  }
	\label{fig:SingleTeffvsOrder}
\end{figure*}

@@
